---
title: "Contributing Spatial Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Contributing Spatial Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning = FALSE}
library(NEFSCspatial)
```

## Adding spatial data to the package.

The initial step is to create an [issue](https://github.com/NEFSC/NEFSC-Spatial/issues/new/choose). The issue should describe the data, and indicate where it is located.

### For collaborators

You will need to clone the repository, create a branch, then a pull request.

  *   Clone the [repo](https://github.com/NEFSC/NEFSC-Spatial)
  *   Set up a new, version controlled, git project in Rstudio
  *   Create a new branch (in Rstudio)
  *   Use one of the supplied functions in the [`data-raw`](https://github.com/NEFSC/NEFSC-Spatial/tree/main/data-raw) folder to convert your shapefile (.shp) file into the required format. If the spatial data is not a shapefile then you will need to include processing scripts.
    * Create documentation for this data set.
    * Commit your files
    * Create a pull request

### For non collaborators

You will need to fork the repository, create a branch, then a pull request.

  *   [Fork](https://github.com/NEFSC/NEFSC-Spatial/fork) the repository to your account
  *   Clone the forked repo
  *   Set up a new, version controlled, git project in Rstudio
  *   Create a new branch
  *   Use one of the supplied [functions](#supplied-functions) in the [`data-raw`](https://github.com/NEFSC/NEFSC-Spatial/tree/main/data-raw) folder to convert your shapefile (.shp) file into the required format. If the spatial data is not a shapefile then you will need to include processing scripts.
    * Create documentation for this data set.
    * Commit your files
    * Create a pull request


Pull requests will be reviewed by a team member

## Supplied functions

*   create_sf_data_from_shp - To convert a shapefile you have stored locally on your machine to sf
*   create_sf_data_from_url - Downloads a zip file from a website (containing shapefile(s)) and converts to sf
*   create_sf_data_from_ftp - Downloads shapefile(s) from a public ftp site and converts to sf
