---
title: "Contributing Spatial Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Contributing Spatial Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning = FALSE}
library(NEFSCspatial)
```

There are two options for adding spatial data into the package.

1. Create an [issue](https://github.com/andybeet/NEFSCspatial/issues) in the repo indicating where the shapefile is located and what it represents 

2. Create a pull request. Follow these steps
    * Clone the [repo](https://github.com/andybeet/NEFSCspatial)
    * Create a new branch
    * Use one of the supplied functions in the `data-raw` folder to convert your .shp file into the required format
    * Commit the .rda file
    * Create a pull request
    Your request will be reviewed by a team member

## Supplied functions

*   create_sf_data_from_shp - To convert a shapefile you have stored locally on your machine to sf
*   create_sf_data_from_url - Downloads a zip file from a website (containing shapefile(s)) and converts to sf
*   create_sf_data_from_ftp - Downloads shapefile(s) from a public ftp site and converts to sf
