---
title: "MDEB datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MDEB datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(NEFSCspatial)
```

The Northeast Fisheries Science Center Marine Development [GIS Data Hub](https://mdeb-nefsc-noaa.hub.arcgis.com/) created by the Marine Development and Ecology Branch (MDEB) host many spatial datasets. The `NEFSCspatial` package provides functions to access these datasets in R and serves them up as `sf` objects.

A current list of all data sets: (see `find_mdeb_datasets()`)

```{r finddatasets, eval = TRUE, echo = FALSE}
datasets <- find_mdeb_datasets() |> 
  dplyr::select(-url)
datasets |> 
  gt::gt()

```

As an example, lets get the Ecosystem Monitoring Survey strata and see what the data looks like.

```{r getecommon, eval = TRUE, echo = TRUE}
ecomon <- get_mdeb_datasets(dataset_name = "Ecosystem Monitoring Survey", id = 1)
ecomon
```

We can then plot any attribute, for example the "REGION"

```{r plotecomon, eval = TRUE, echo = TRUE, fig.alt="ECOMON Region plot"}
ecomon |> 
  ggplot2::ggplot() + 
  ggplot2::geom_sf(ggplot2::aes(fill = REGION))

```
