---
title: "MDEB datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MDEB datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(NEFSCspatial)
```

The Northeast Fisheries Science Center Marine Development [GIS Data Hub](https://mdeb-nefsc-noaa.hub.arcgis.com/) created by the Marine Development and Ecology Branch (MDEB) host many spatial datasets. The `NEFSCspatial` package provides access to these datasets and serves them up as `sf` objects.

A current list of all data sets included in the package:

```{r finddatasets, eval = TRUE, echo = FALSE}
# url of the MDEB GIS Data Hub search API
mdeb_hub = "https://mdeb-nefsc-noaa.hub.arcgis.com/api/search/v1/collections/all/items"
# scrape json to get all feature services
catalog_items <- mdeb_hub |>
  jsonlite::fromJSON()
# count the number of available services
num_items <- catalog_items$numberMatched
# pull all feature service items (API default = 10)
catalog_items_v2 <- paste0(mdeb_hub, "?limit=", num_items) |>
  jsonlite::fromJSON()
# extract metadata properties
available_datasets <- catalog_items_v2$features$properties |>
  dplyr::filter(grepl("FeatureServer", url)) |>
  dplyr::select(title, url)
# format metadata for each feature service as json
available_dataset_layers <- available_datasets |>
  dplyr::mutate(layerurl = paste0(url, "?f=pjson"))
# create a new data frame to store the results
dataset_metadata <- NULL
# find if there are multiple feature layers per service
for (idataset in 1:nrow(available_dataset_layers)) {
  dataset_url <- available_dataset_layers[idataset, ]
  dataset_json_url <- dataset_url$layerurl
  # request the json format for the metadata
  wp <- dataset_json_url |>
    jsonlite::fromJSON()
  # create tibble for output
  av = wp$layers |>
    dplyr::mutate(dataset_url) |>
    dplyr::mutate(url = paste0(url, '/', id)) |>
    dplyr::select(title, name, id, url) |>
    dplyr::as_tibble()
  dataset_metadata <- dplyr::bind_rows(dataset_metadata, av)
}

  
dataset_metadata |>
  dplyr::select(-url) |> 
  dplyr::mutate(dataset_name = tolower(gsub("SMIT_", "", dataset_metadata$name))) |>
  dplyr::select(title, dataset_name) |>
  gt::gt()

```


We can then plot any attribute, for example the "SUBSTRATA" attribute of the `gombll_substrata` dataset:

```{r plotecomon, eval = TRUE, echo = TRUE, fig.alt="Gulf of Maine Bottom Longline Survey substrata plot"}
gombll_substrata |> 
  ggplot2::ggplot() + 
  ggplot2::geom_sf(ggplot2::aes(fill = SUBSTRATA))

```
