---
title: "MDEB datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MDEB datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(NEFSCspatial)
source(here::here("data-raw/find_mdeb_data.R"))
source(here::here("data-raw/get_mdeb_data.R"))

```

The Northeast Fisheries Science Center Marine Development [GIS Data Hub](https://mdeb-nefsc-noaa.hub.arcgis.com/) created by the Marine Development and Ecology Branch (MDEB) host many spatial datasets. The `NEFSCspatial` package provides access to these datasets and serves them up as `sf` objects.

A current list of all data sets included in the package:

```{r finddatasets, eval = TRUE, echo = FALSE}
datasets <- find_mdeb_data() |> 
  dplyr::select(-url)
datasets |> 
  dplyr::mutate(dataset_name = tolower(gsub("SMIT_", "", datasets$name))) |> 
  dplyr::select(title, dataset_name) |> 
  gt::gt()

```


We can then plot any attribute, for example the "SUBSTRATA" attribute of the `gombll_substrata` dataset:

```{r plotecomon, eval = TRUE, echo = TRUE, fig.alt="ECOMON Region plot"}
gombll_substrata |> 
  ggplot2::ggplot() + 
  ggplot2::geom_sf(ggplot2::aes(fill = SUBSTRATA))

```
